RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-12 paper.tex
working

@@

% limitations
Previous studies have pointed out difficulties in achieving production-level
flexibility, scalability and maintainability with experimental code created
by data analysts. These properties cannot be ensured by any programming environment,
but suitable tools can help well-intentioned analysts and programmers to create
robust applications with less effort.

>>>>

\cite{Keim:2008:VAS}

@@

% limitations
Previous studies have pointed out difficulties in achieving the flexibility,
scalability and maintainability expected of production software with experimental
code created by data analysts.
These properties cannot be ensured by any programming environment,
but suitable tools can help well-motivated analysts and programmers to create
robust applications with much less effort.
